NMRlipids IV: Headgroup \& glycerol backbone structures, and cation binding in bilayers with PS lipids

### 2018-06-28 Manuscript/manuscriptPS.tex
Add abstract

\begin{abstract}
  % insert abstract here
  Primarily measured but also simulated NMR order parameters will be collected also for other than phophatidylcholine
  (these are discussed in NMRlipids I) headgroup. The information will be used to understand structural differences between 
  different lipid molecules in bilayers.
\end{abstract}

@@

\subsection{Molecular dynamics simulations}
Molecular dynamics simulation data was collected using
the Open Collaboration method \cite{botan15}.
The NMRlipids project blog (\url{nmrlipids.blogspot.fi}) and
the GitHub repository (\url{github.com/NMRLipids/NMRlipidsIVotherHGs})
were used as the communication platforms.
The simulated systems are listed in Table \ref{IONsystems} and
simulation details are given in the SI.
The simulation data is also indexed in the
searchable database (\url{nmrlipids.fi}),
and in the NMRlipids/MATCH GitHub repository (\url{https://github.com/NMRLipids/MATCH}).  

@@

>>>>

\begin{abstract}
  % insert abstract here
Phosphatidylserine (PS) is the most common negatively
charged lipid in eykaryotic membranes.
PS lipids interact with signaling and other proteins via
electrostatic interactions and direct binding, and induce
membrane fusion and phase separation together with calcium ions.
Molecular details of these phenomena are not well understood
because accurate models to interpret the experimental data has not
been available. Here, we collect a set of experimental NMR data which
could be used together with molecular dynamics (MD) simulations
to interpret the lipid headgroup structures and details of ion binding
in pure and mixed PS and PS:PC lipid bilayers. Aiming to interpret the
data, we use the open collaboration method to go through the available MD simulation models for PS lipids.
However, none of the models reproduce the experimental data with sufficient
accuracy to interpet the structural details of lipid headgroups or
ion binding details in lipid bilayers containing PS lipids.
In contrast to PC lipids, the tested MD simulation models do not
correctly reproduce the qualitative response of PS lipid headgroups
to the bound ions or changes in the lipid composition. 
Our results pave the way for the model improvement to correctly
describe negatively charged membranes and their interactions with ions.
\end{abstract}

@@

@@

\subsection{Molecular dynamics simulations}
Molecular dynamics simulation data was collected using
the Open Collaboration method \cite{botan15}.
The NMRlipids project blog (\url{nmrlipids.blogspot.fi}) and
the GitHub repository (\url{github.com/NMRLipids/NMRlipidsIVotherHGs})
were used as the communication platforms.
The simulated systems are listed in Table \ref{IONsystems} and
simulation details are given in the SI.
The simulation data is also indexed in the
searchable database (\url{nmrlipids.fi}),
and in the NMRlipids/MATCH GitHub repository (\url{https://github.com/NMRLipids/MATCH}).
